Pulmonary acini exhibit complex changes during postnatal rat lung development

### 2021-07-12 manuscript.tex
Update caption/details of Fig01 [ci skip]
This build is based on
https://github.com/habi/acinar-analysis-manuscript/commit/a65dd66b6e24c81920a739bd387cabf8cdd9924f.

This commit was created by the following CI build and job:
https://github.com/habi/acinar-analysis-manuscript/commit/a65dd66b6e24c81920a739bd387cabf8cdd9924f/checks
https://github.com/habi/acinar-analysis-manuscript/runs/1023083462

A preprint of this manuscript is available on \emph{bioRxiv} with the DOI \href{https://doi.org/10.1101/786681}{10.1101/786681}.
It has been submited to \href{https://journals.plos.org/plosone/}{\emph{PLOS ONE}}.
The manuscript \href{https://github.com/habi/acinar-analysis-manuscript/compare/5e778036e316c47b8bac4ce50086b191a7e3707a...ee755381aa3d6b20245ee2cd1fae56dc108d7d30}{has been updated} since submission.

This manuscript
(\href{https://habi.github.io/acinar-analysis-manuscript/v/ee755381aa3d6b20245ee2cd1fae56dc108d7d30/}{permalink})
was automatically generated
from \href{https://github.com/habi/acinar-analysis-manuscript/tree/ee755381aa3d6b20245ee2cd1fae56dc108d7d30}{habi/acinar-analysis-manuscript@ee75538}
on July 6, 2021.

@@

\begin{itemize}
\item
  \textbf{David Haberthür}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3388-9187}{0000-0003-3388-9187}
  · \href{mailto:haberthuer@ana.unibe.ch?subject=Feedback\%20regarding\%20the\%20acinus\%20manuscript\%20(ee75538)}{haberthuer@ana.unibe.ch}
  · \includegraphics{images/github.svg}
  \href{https://github.com/habi}{habi}
  · \includegraphics{images/twitter.svg}
  \href{https://twitter.com/habi}{habi}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Eveline Yao}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Sébastien F. Barré}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Tiziana P. Cremona}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-0061-9578}{0000-0003-0061-9578}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Stefan A. Tschanz}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3880-4437}{0000-0003-3880-4437}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Johannes C. Schittny}✉
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-4025-3961}{0000-0003-4025-3961}
  · \href{mailto:schittny@ana.unibe.ch?subject=Feedback\%20regarding\%20the\%20acinus\%20manuscript\%20(ee75538)}{schittny@ana.unibe.ch}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\end{itemize}

@@

For the present manuscript, we extracted single acini from three-dimensional data, acquired without destroying the samples.
Details of this semi-automatic extraction of the rat acini are described by Haberthür et al.~{[}\protect\hyperlink{ref-7YLeeyu}{21}{]}.
Individual acini were extracted from the tomographic data with a custom image processing network established in \href{https://www.mevislab.de/}{MeVisLab} (version 2.1, 2010-07-26 release, MeVis Medical Solutions and Fraunhofer MEVIS-Institute for Medical Image Computing, Bremen, Germany).
To isolate individual acini, we followed the airway tree in the data and manually placed disk-shaped segmentation stoppers at the acinus entrances.
Thus, acini were selected independently of their size and only based on their location in the airway tree.
The acinus extraction was performed by segmenting the acinus volume with a gray-level threshold-based region growing algorithm with a seed point perpendicular to the manually placed segmentation stopper.
Each individual acinus was then exported as a single DICOM file for portability.
For each acinus, its exported DICOM file contained the segmented acinus overlaid with the original background for further analysis.
Example images from the DICOM files are shown in the bottom row of figure~\ref{fig:01}.

@@

\begin{figure}
\hypertarget{fig:01}{%
\centering
\includegraphics{images/fig01.png}
\caption{Example images for each of the assessed time points.
A--D: Representative light microscopy images.
E--H: One slice of the tomographic data sets.
I--L: Middle slice of one of the extracted acini.
The extracted acinus is overlaid on the tomographic dataset.
Panels J and K also show the segmentation stopper at the left border of the image.
The shown images correspond to the middle slice of the full data sets used for the stereological analysis.
The scale bar was burnt in during preparation of the image stacks and is 100~μm long.
Panels A, E \& I: Day 4.
Panels B, F \& J: Day 10.
Panels C, G \& K: Day 21.
Panels D, H \& L: Day 60.
Panel M: Three-dimensional visualization of the acini shown in panels I--L.}\label{fig:01}
}
\end{figure}

>>>>

A preprint of this manuscript is available on \emph{bioRxiv} with the DOI \href{https://doi.org/10.1101/786681}{10.1101/786681}.
It has been submited to \href{https://journals.plos.org/plosone/}{\emph{PLOS ONE}}.
The manuscript \href{https://github.com/habi/acinar-analysis-manuscript/compare/5e778036e316c47b8bac4ce50086b191a7e3707a...a65dd66b6e24c81920a739bd387cabf8cdd9924f}{has been updated} since submission.

This manuscript
(\href{https://habi.github.io/acinar-analysis-manuscript/v/a65dd66b6e24c81920a739bd387cabf8cdd9924f/}{permalink})
was automatically generated
from \href{https://github.com/habi/acinar-analysis-manuscript/tree/a65dd66b6e24c81920a739bd387cabf8cdd9924f}{habi/acinar-analysis-manuscript@a65dd66}
on July 12, 2021.

@@

\begin{itemize}
\item
  \textbf{David Haberthür}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3388-9187}{0000-0003-3388-9187}
  · \href{mailto:haberthuer@ana.unibe.ch?subject=Feedback\%20regarding\%20the\%20acinus\%20manuscript\%20(a65dd66)}{haberthuer@ana.unibe.ch}
  · \includegraphics{images/github.svg}
  \href{https://github.com/habi}{habi}
  · \includegraphics{images/twitter.svg}
  \href{https://twitter.com/habi}{habi}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Eveline Yao}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Sébastien F. Barré}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Tiziana P. Cremona}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-0061-9578}{0000-0003-0061-9578}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Stefan A. Tschanz}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3880-4437}{0000-0003-3880-4437}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Johannes C. Schittny}✉
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-4025-3961}{0000-0003-4025-3961}
  · \href{mailto:schittny@ana.unibe.ch?subject=Feedback\%20regarding\%20the\%20acinus\%20manuscript\%20(a65dd66)}{schittny@ana.unibe.ch}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\end{itemize}

@@

For the present manuscript, we extracted single acini from three-dimensional data, acquired without destroying the samples.
Details of this semi-automatic extraction of the rat acini are described by Haberthür et al.~{[}\protect\hyperlink{ref-7YLeeyu}{21}{]}.
Individual acini were extracted from the tomographic data with a custom image processing network established in \href{https://www.mevislab.de/}{MeVisLab} (version 2.1, 2010-07-26 release, MeVis Medical Solutions and Fraunhofer MEVIS-Institute for Medical Image Computing, Bremen, Germany).
To isolate individual acini, we followed the airway tree in the data and manually placed disk-shaped segmentation stoppers at the acinus entrances.
Thus, acini were selected independently of their size and only based on their location in the airway tree.
The acinus extraction was performed by segmenting the acinus volume with a gray-level threshold-based region growing algorithm with a seed point perpendicular to the manually placed segmentation stopper.
Each individual acinus was then exported as a single DICOM file for portability.
For each acinus, its exported DICOM file contained the segmented acinus overlaid with the original background for further analysis.
Example images from the DICOM files are shown in panels I--L of figure~\ref{fig:01}.

@@

\includegraphics{images/fig01.png}
Panels A, E, I \& M: Day 4.
Panels B, F, J \& N: Day 10.
Panels C, G, K \& O: Day 21.
Panels D, H, L \& P: Day 60.{]}(images/fig01.png)\{\#fig:01\}
